Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-15 paper.tex
put a *few* numbers back in the conclusions

Significant speedups in shallow SIMD-vectorized execution over a parallel OpenMP code were demonstrated for evaluations of the chemical kinetic source-term and sparse\slash dense Jacobian.
Sparse Jacobian evaluation was slower than dense evaluation on all CPU\slash GPU platforms due to indirect lookup requirements in array indexing, however the shallow-vectorized OpenCL code was less adversely affected than OpenMP.
Further, analytical Jacobian evaluation was significantly faster than a first-order finite-difference based approach on all platforms.
Finally, the performance of dense analytical-Jacobian evaluation in this new version of \texttt{pyJac} was compared to the previous version~\cite{pyjac16}; OpenMP evaluation on the CPU was slightly slower for the smallest chemical model, but significantly faster for the larger models, while the shallow-vectorized OpenCL code was faster than the previous version over all chemical models.

>>>>

\todo{kyle double check that this paragraph reads well}
\revise{Significant speedups in shallow SIMD-vectorized execution over a parallel OpenMP code were demonstrated for evaluations of the chemical kinetic source-term and sparse\slash dense Jacobian: up to \SI{4.09}{$\times$}, \SI{4.23}{$\times$} and \SI{9.44}{$\times$}, respectively, on an \avx/-capable CPU.}
\revise{Sparse Jacobian evaluation was slower than dense evaluation on all CPU\slash GPU platforms due to indirect lookup requirements in array indexing, however the shallow-vectorized OpenCL code was less adversely affected than OpenMP.}
\revise{Further, analytical Jacobian evaluation was significantly faster than a first-order finite-difference based approach on all platforms.}
\revise{Finally, the performance of dense analytical-Jacobian evaluation in this new version of \texttt{pyJac} was compared to the previous version~\cite{pyjac16}; OpenMP evaluation on the CPU was moderately slower for the smallest chemical model (e.g., \SI{1.79}{$\times$} on the \avx/ CPU), but significantly faster (up to \SI{10.19}{$\times$}) for the larger models, while the shallow-vectorized OpenCL code was faster than the previous version over all chemical models, reaching speedups of \SI{19.56}{$\times$}.}
